\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-07-03 cubble.Rmd
section 3.2

The cubble workflow can be easily incorporated into an interactive graphics pipeline (e.g., @buja1988elements; @buja1996interactive;  @sutherland2000orca; @xie2014reactive; @cheng2016enabling). The cubble data structure simplifies data pre-processing and prepares the ingredient for interactive graphics. Specifically, the spatial and temporal cubble correspond to the spatial and temporal visualisation, such as a map or a time series plot, that can be linked. Figure \ref{fig:illu-interactive} illustrates the linking mechanism between a map and multiple time series in the \pkg{crosstalk} [@crosstalk] package. When a user selects a location on the map as shown on panel (a), the corresponding site is highlighted. This selection activates a row in the spatial cubble, which is then connected to the temporal cubble, resulting in the selection of all observations with the same ID as depicted in panel (b). Consequently the temporal cubble highlights the corresponding series in the time series plot displayed in panel (c). The linking can also be initiated from the time series plot by selecting points on the time series graph. This action selects rows with the same ID in the temporal cubble and the corresponding row in the spatial cubble so that points can be highlight on the map.

>>>>

The cubble workflow neatly allows building an interactive graphics pipeline (e.g., @buja1988elements; @buja1996interactive;  @sutherland2000orca; @xie2014reactive; @cheng2016enabling), simplifying the data pre-processing and preparing the ingredients for linked plots. Specifically, the spatial and temporal cubble correspond to the spatial and temporal visualisation, such as a map or a time series plot, that can be linked using functionality in the \pkg{crosstalk} [@crosstalk] package.

Figure \ref{fig:illu-interactive} illustrates the linking mechanism between a map and multiple time series. When a user selects a location on the map as shown on panel (a), the corresponding site is highlighted. This selection activates a row in the spatial cubble, which is then connected to the temporal cubble, resulting in the selection of all observations with the same ID as depicted in panel (b). Consequently the temporal cubble highlights the corresponding series in the time series plot displayed in panel (c). The linking can also be initiated from the time series plot by selecting points on the time series graph. This action selects rows with the same ID in the temporal cubble and the corresponding row in the spatial cubble so that points can be highlight on the map.

### 2023-07-03 cubble.tex
section 3.2

The cubble workflow can be easily incorporated into an interactive graphics pipeline (e.g., \citet{buja1988elements}; \citet{buja1996interactive}; \citet{sutherland2000orca}; \citet{xie2014reactive}; \citet{cheng2016enabling}). The cubble data structure simplifies data pre-processing and prepares the ingredient for interactive graphics. Specifically, the spatial and temporal cubble correspond to the spatial and temporal visualisation, such as a map or a time series plot, that can be linked. Figure \ref{fig:illu-interactive} illustrates the linking mechanism between a map and multiple time series in the \pkg{crosstalk} \citep{crosstalk} package. When a user selects a location on the map as shown on panel (a), the corresponding site is highlighted. This selection activates a row in the spatial cubble, which is then connected to the temporal cubble, resulting in the selection of all observations with the same ID as depicted in panel (b). Consequently the temporal cubble highlights the corresponding series in the time series plot displayed in panel (c). The linking can also be initiated from the time series plot by selecting points on the time series graph. This action selects rows with the same ID in the temporal cubble and the corresponding row in the spatial cubble so that points can be highlight on the map.

>>>>

The cubble workflow neatly allows building an interactive graphics pipeline (e.g., \citet{buja1988elements}; \citet{buja1996interactive}; \citet{sutherland2000orca}; \citet{xie2014reactive}; \citet{cheng2016enabling}), simplifying the data pre-processing and preparing the ingredients for linked plots. Specifically, the spatial and temporal cubble correspond to the spatial and temporal visualisation, such as a map or a time series plot, that can be linked using functionality in the \pkg{crosstalk} \citep{crosstalk} package.

Figure \ref{fig:illu-interactive} illustrates the linking mechanism between a map and multiple time series. When a user selects a location on the map as shown on panel (a), the corresponding site is highlighted. This selection activates a row in the spatial cubble, which is then connected to the temporal cubble, resulting in the selection of all observations with the same ID as depicted in panel (b). Consequently the temporal cubble highlights the corresponding series in the time series plot displayed in panel (c). The linking can also be initiated from the time series plot by selecting points on the time series graph. This action selects rows with the same ID in the temporal cubble and the corresponding row in the spatial cubble so that points can be highlight on the map.
